\chapter{Bibliographie}

\begin{thebibliography}{1}
\subsection*{Détection d'anomalies}
\bibitem{Breiman}
BREIMAN, Leo. 
\emph{Random forests.}
Machine learning, 2001, vol. 45, no 1, p. 5-32.

\bibitem{BreunigM}
	 BREUNIG, Markus M., KRIEGEL, Hans-Peter, NG, Raymond T., et al. 
	 \emph{LOF: identifying density-based local outliers.} 
	 In : ACM sigmod record. ACM, 2000. p. 93-104.
	  
\bibitem{ChandolaV}	  
	  CHANDOLA, Varun, BANERJEE, Arindam, et KUMAR, Vipin. 
	  \emph{Anomaly detection: A survey.}
	   ACM computing surveys (CSUR), 2009, vol. 41, no 3, p. 15.
	   
\bibitem{MalhotraP}	  
	MALHOTRA, Pankaj, VIG, Lovekesh, SHROFF, Gautam, et al.
	\emph{Long short term memory networks for anomaly detection in time series.} 
	In : Proceedings. Presses universitaires de Louvain, 2015. p. 89.
	   
\bibitem{KeohgE}    
   KEOGH, Eamonn, LONARDI, Stefano, et CHIU, Bill'Yuan-chi'. 
   \emph{Finding surprising patterns in a time series database in linear time and space.} In : Proceedings of the eighth ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2002. p. 550-556.
	   
\bibitem{LiZ} 	
Li, Z., Li, Z., Yu, N., Wen, S. 	   
	   \emph{Locality-Based Visual Outlier Detection Algorithm for Time Series}
	   Security and Communication Networks, 2017.  
\bibitem{ChenC} 	   
	Chen, C., Liu, L. M. (1993).
\emph{Joint estimation of model parameters and outlier effects in time series.}
Journal of the American Statistical Association, 88(421), 284-297.	   

\bibitem{DingH} 	
DING, Hui, TRAJCEVSKI, Goce, SCHEUERMANN, Peter, et al. 
\emph{Querying and mining of time series data: experimental comparison of representations and distance measures.}
 Proceedings of the VLDB Endowment, 2008, vol. 1, no 2, p. 1542-1552.

\bibitem{BClementine}
BARREYRE, Clementine
\emph{Statistiques en grande dimension pour la détection d'anomalies dans les données fonctionnelles issues des satellites. 2018. Thèse de doctorat. INSA de Toulouse.}

\subsection*{Décomposition en ondelettes}
\bibitem{StMallat}
	  Stéphane Mallat,
	  \emph{A Wavelet Tour of Signal Processing}.
	  Elsevier, 
	  1999.
	  
\bibitem{JBigot}
	Jérémie Bigot,
	\emph{Analyse par ondelettes}
	Université Paul Sabatier,
	2009		  
\bibitem{AGraps}
	Amara Graps
	\emph{An Introduction to Wavelets}
	 IEEE computational science and engineering, 1995, vol. 2, no 2, p. 50-61,
	 1995.
\bibitem{Cchui}
		Charles K Chui
      	\emph{An Introduction to Wavelets}
      	 Elsevier, 2016.
\bibitem{GRama}
	GENÇAY, Ramazan, SELÇUK, Faruk, et WHITCHER, Brandon J
	 \emph{An introduction to wavelets and other filtering methods in finance and economics} 			      Elsevier, 2001.
\bibitem{WojPrz} 
  WOJTASZCZYK, Przemyslaw. 
  \emph{A mathematical introduction to wavelets.}
   Cambridge University Press, 1997.
\bibitem{GStrang}  
	STRANG, Gilbert et NGUYEN, Truong.
	\emph{Wavelets and filter banks.}
	 SIAM, 1996.
\bibitem{SMalla92} 	 
MALLAT, Stephane et HWANG, Wen Liang.
\emph{Singularity detection and processing with wavelets. IEEE transactions on information theory} X vol. 38, no 2, p. 617-643, 1992.  

\bibitem{GaoR}  
Gao, R. X., Yan, R. (2010)
\emph{Wavelets: Theory and applications for manufacturing.} 
Springer Science \& Business Media.   

\bibitem{Mo}
Mo Fan
\emph{Wavelets and artificial neural networks in power system transient classification and short-term power load prediction}, 2012
Master thesis, University of Manitoba   

\subsection*{Décomposition par méthodes adaptatives}
\bibitem{NAM}
Nicolas Di Palma, Alain Batailly, Mathias Legrand.
\emph{Méthodes de traitement du signal par décomposition en modes empiriques. [Rapport de recherche] Université McGill. 2018. <hal-01819670>}

\bibitem{EMD-maths}
N. E. Huang, Z. Shen, S. R. Long, M. C. Wu, H. H. Shih, Q. Zheng, N.-C. Yen, C. C. Tung, H. H. Liu.
\emph The empirical mode decomposition and the Hilbert spectrum for nonlinear and non-stationary time series analysis, Proceedings of the RoyalSociety of London A: Mathematical, Physical and Engineering Sciences 454 (1971) (1998) 903–995.

\bibitem{test_LMD}
Y. Yang, J. Cheng, K. Zhang.
\emph{An ensemble local means decomposition method and its application to local rub-impact fault
diagnosis of the rotor systems, Measurement 45 (3) (2012) 561–570}


\bibitem{MFD}
 Y. Zhang, C. Bingham, Z. Yang, B. W.-K. Ling, M. Gallimore.
 \emph{Machine fault detection by signal denoising—with application to
industrial gas turbines, Measurement 58 (2014) 230–240.}

\bibitem{Guler}
GULER, Inan et UBEYLI, Elif Derya
\emph{ECG beat classifier designed by combined neural network model.}
 Pattern recognition, 2005, vol. 38, no 2, p. 199-208.
 

\subsection*{Méthodes de séparation de sources}
\bibitem{JialiM}
Jiali Mei.
\emph{Time series recovery and prediction with regression-enhanced nonnegative matrix factoriza-
tion applied to electricity consumption. Statistics [math.ST].} Université Paris-Saclay, 2017.

\bibitem{Sümbül}
Gencer Sümbül
\emph{Finding Underlying Trends and Clustering of Time Series with Non-negative Matrix Factorization and K-Means}
\url{http://gencersumbul.bilkent.edu.tr/pdf/time_series_clustering.pdf}

\bibitem{MeiCastroGoudeAzaïsHébrail}
Jiali Mei, Yohann De Castro, Yannig Goude, Jean-Marc Azaïs, and Georges Hébrail
\emph{Nonnegative matrix factorization with side information for time series recovery and prediction}
\url{https://ydecastro.github.io/research/paper18.pdf}

\bibitem{Nguyen}
Phuoc Nguyen, Dat Tran, Xu Huang and Dharmendra Sharma
\emph{A Proposed Feature Extraction Method for EEG-based Person Identification} 
Faculty of Information Sciences and Engineering University of Canberra, ACT 2601, Australia 
\url{https://core.ac.uk/download/pdf/30346641.pdf}

\bibitem{Cheung}
Vincent C. K. Cheung, Karthik Devarajan, Giacomo Severini, Andrea Turolla, and Paolo Bonato
\emph{Decomposing Time Series Data by a Non-negative Matrix Factorization Algorithm with Temporally Constrained Coefficients}
\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5593271/}


\subsection*{Références liées au domaine médical}
\bibitem{Luz}
Luz, Eduardo José da S., et al. 
\emph{ECG-based heartbeat classification for arrhythmia detection: A survey.} Computer methods and programs in biomedicine 127 (2016): 144-164.

\bibitem{INCE}
INCE, Turker, KIRANYAZ, Serkan, et GABBOUJ, Moncef.
\emph{A generic and robust system for automated patient-specific classification of ECG signals.} IEEE Transactions on Biomedical Engineering, 2009, vol. 56, no 5, p. 1415-1426.

\subsection*{Références liées à la production d'énergie et panneaux solaires}

\bibitem{FaultSolarPanel}
LIVERA, Andreas, THERISTIS, Marios, MAKRIDES, George, et al.
\emph{Recent advances in failure diagnosis techniques based on performance data analysis for grid-connected photovoltaic systems.} Renewable Energy, 2018.

\bibitem{Mao}
Mao, Peilin L., and Raj K. Aggarwal. 
\emph{A novel approach to the classification of the transient phenomena in power transformers using combined wavelet transform and neural network.} IEEE Transactions on Power Delivery 16.4 (2001): 654-660.

\bibitem{ChenZ}
Chen, Zhicong, et al. 
\emph{Random forest based intelligent fault diagnosis for PV arrays using array voltage and string currents.} Energy Conversion and Management 178 (2018): 250-264.

\bibitem{ferhartUc}
UCAR, Ferhat, ALCIN, Omer F., DANDIL, Besir, et al.
\emph{Power quality event detection using a fast extreme learning machine. }
Energies, 2018, vol. 11, no 1, p. 145.

\bibitem{MMostafa}
Majidpour, Mostafa, et al. 
\emph{Fast Univariate Time Series Prediction of Solar Power for Real-Time Control of Energy Storage System.} Forecasting 1.1 (2018): 107-120.

\bibitem{JavedW}
Javed, W., Wubulikasimu, Y., Figgis, B., \& Guo, B. (2017). 
\emph{Characterization of dust accumulated on photovoltaic panels in Doha, Qatar. Solar Energy, 142, 123-135.}

\bibitem{FboxPlot}
Sun, Ying, and Marc G. Genton. 
\emph{Functional boxplots." Journal of Computational and Graphical Statistics} 20.2 (2011): 316-334.

\end{thebibliography}	
